---
title: "Multivariate-Analysis-Sites"
author: "Aji John"
date: "10/10/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
```
## Objective

Goal is to test microclimatic variation hypthesis in long-term forests. i.e. There is a significant microclimatic variations that can be found under forest canopies. 

## Study system

Mt Rainier is known to house vary distinctive microclimates, for our study we chose 5 sites along an elvational gradient on the southside of Mt Rainier.

# Data Preparation

Find monthly minimum temperatures for all the 5 sites

```{r }
#Site TO04

TO04 <- read_csv("./data/TO04-S1.csv",skip = 1)
#rename columns
col_names <- c("index","Date_Time", "Temp", "Intensity", "Coupler" , "HostConnected","Stopped",  "EndOfFile") 
colnames(TO04) <- col_names
# fix the date
TO04$datetime <- as_datetime(TO04$Date_Time,format='%m/%d/%y %r',tz="America/Los_Angeles")
#convery date from Posixlt to Posixct - Dplyr requirement
TO04$datetime <- as.POSIXct(TO04$datetime)
#create summary metrics by month
TO04$hr <-strftime(TO04$datetime,'%H')
TO04$min <-strftime(TO04$datetime,'%M')
TO04$month <- strftime(TO04$datetime,'%m')
TO04$day <- strftime(TO04$datetime,'%d')

df_TO04 <- TO04 %>% group_by(month,day) %>%
  mutate(min_daily= min(Temp),max_daily= max(Temp)) %>% 
  group_by(month) %>% 
  mutate(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  filter(month %in% c("06","07","08")) %>%
  summarise(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  select(c("month","min_jja")) %>% 
  spread(key = "month",value = "min_jja") %>%  mutate(site="TO04") %>% 
  as.data.frame()

#Site AE10

AE10 <- read_csv("./data/AE10-S1.csv",skip = 1)
#rename columns
col_names <- c("index","Date_Time", "Temp", "Intensity", "Coupler" , "HostConnected","Stopped",  "EndOfFile") 
colnames(AE10) <- col_names
AE10 <- AE10[,col_names]
# fix the date
AE10$datetime <- as_datetime(AE10$Date_Time,format='%m/%d/%y %r',tz="America/Los_Angeles")
#convery date from Posixlt to Posixct - Dplyr requirement
AE10$datetime <- as.POSIXct(AE10$datetime)
#create summary metrics by month
AE10$hr <-strftime(AE10$datetime,'%H')
AE10$min <-strftime(AE10$datetime,'%M')
AE10$month <- strftime(AE10$datetime,'%m')
AE10$day <- strftime(AE10$datetime,'%d')

#missing june
df_AE10 <- AE10 %>% 
  group_by(month,day) %>%
  mutate(min_daily= min(Temp),max_daily= max(Temp)) %>% 
  group_by(month) %>% 
  mutate(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  filter(month %in% c("06","07","08")) %>%
  summarise(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  select(c("month","min_jja")) %>% 
  spread(key = "month",value = "min_jja") %>%  mutate(site="AE10") %>% 
  as.data.frame()

# add "NA" for june
df_AE10$"06" <- NA
#Site AG05

AG05 <- read_csv("./data/AG05-S1.csv",skip = 1)
#rename columns
col_names <- c("index","Date_Time", "Temp", "Intensity", "Coupler" , "HostConnected","Stopped",  "EndOfFile") 
colnames(AG05) <- col_names
AG05 <- AG05[,col_names]
# fix the date
AG05$datetime <- as_datetime(AG05$Date_Time,format='%m/%d/%y %r',tz="America/Los_Angeles")
#convery date from Posixlt to Posixct - Dplyr requirement
AG05$datetime <- as.POSIXct(AG05$datetime)
#create summary metrics by month
AG05$hr <-strftime(AG05$datetime,'%H')
AG05$min <-strftime(AG05$datetime,'%M')
AG05$month <- strftime(AG05$datetime,'%m')
AG05$day <- strftime(AG05$datetime,'%d')

#
df_AG05 <- AG05 %>% 
  group_by(month,day) %>%
  mutate(min_daily= min(Temp),max_daily= max(Temp)) %>% 
  group_by(month) %>% 
  mutate(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  filter(month %in% c("06","07","08")) %>%
  summarise(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  select(c("month","min_jja")) %>% 
  spread(key = "month",value = "min_jja") %>%  mutate(site="AG05") %>% 
  as.data.frame()

#Site AM16

AM16 <- read_csv("./data/AM16-S1.csv",skip = 1)
#rename columns
col_names <- c("index","Date_Time", "Temp", "Intensity", "Coupler" , "HostConnected","Stopped",  "EndOfFile") 
colnames(AM16) <- col_names
AM16 <- AM16[,col_names]
# fix the date
AM16$datetime <- as_datetime(AM16$Date_Time,format='%m/%d/%y %r',tz="America/Los_Angeles")
#convery date from Posixlt to Posixct - Dplyr requirement
AM16$datetime <- as.POSIXct(AM16$datetime)
#create summary metrics by month
AM16$hr <-strftime(AM16$datetime,'%H')
AM16$min <-strftime(AM16$datetime,'%M')
AM16$month <- strftime(AM16$datetime,'%m')
AM16$day <- strftime(AM16$datetime,'%d')

#
df_AM16 <- AM16 %>% 
  group_by(month,day) %>%
  mutate(min_daily= min(Temp),max_daily= max(Temp)) %>% 
  group_by(month) %>% 
  mutate(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  filter(month %in% c("06","07","08")) %>%
  summarise(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  select(c("month","min_jja")) %>% 
  spread(key = "month",value = "min_jja") %>%  mutate(site="AM16") %>% 
  as.data.frame()

#Site AV06

AV06 <- read_csv("./data/AV06-S1.csv",skip = 1)
#rename columns
col_names <- c("index","Date_Time", "Temp", "Intensity", "Coupler" , "HostConnected","Stopped",  "EndOfFile") 
colnames(AV06) <- col_names
AV06 <- AV06[,col_names]
# fix the date
AV06$datetime <- as_datetime(AV06$Date_Time,format='%m/%d/%y %r',tz="America/Los_Angeles")
#convery date from Posixlt to Posixct - Dplyr requirement
AV06$datetime <- as.POSIXct(AV06$datetime)
#create summary metrics by month
AV06$hr <-strftime(AV06$datetime,'%H')
AV06$min <-strftime(AV06$datetime,'%M')
AV06$month <- strftime(AV06$datetime,'%m')
AV06$day <- strftime(AV06$datetime,'%d')

#
df_AV06 <- AV06 %>% 
  group_by(month,day) %>%
  mutate(min_daily= min(Temp),max_daily= max(Temp)) %>% 
  group_by(month) %>% 
  mutate(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  filter(month %in% c("06","07","08")) %>%
  summarise(min_jja = mean(min_daily,na.rm = T),max_jja = max(max_daily,na.rm = T)) %>%
  select(c("month","min_jja")) %>% 
  spread(key = "month",value = "min_jja") %>%  mutate(site="AV06") %>% 
  as.data.frame()

#site characteristics
```
#Combine into 1 dataframe

```{r , echo=FALSE}
df_sites <- rbind(df_AE10,df_AG05,df_AM16,df_AV06,df_TO04)
```



#Add additional site characteristics
```{r , echo=FALSE}
sites_spatial <- read_csv("./data/sites")
df_sites$long <- 0
df_sites$lat <- 0
df_sites[df_sites$site=="AV06",]$long<- sites_spatial %>% 
    filter(site %in% c("AV06")) %>% select("long") %>%as.numeric()
df_sites[df_sites$site=="AV06",]$lat<- sites_spatial %>% 
    filter(site %in% c("AV06")) %>% select("lat")

df_sites[df_sites$site=="AE10",]$long<- sites_spatial %>% 
    filter(site %in% c("AE10")) %>% select("long")
df_sites[df_sites$site=="AE10",]$lat<- sites_spatial %>% 
    filter(site %in% c("AE10")) %>% select("lat")

df_sites[df_sites$site=="AG05",]$long<- sites_spatial %>% 
    filter(site %in% c("AG05")) %>% select("long")
df_sites[df_sites$site=="AG05",]$lat<- sites_spatial %>% 
    filter(site %in% c("AG05")) %>% select("lat")

df_sites[df_sites$site=="AM16",]$long<- sites_spatial %>% 
    filter(site %in% c("AM16")) %>% select("long")
df_sites[df_sites$site=="AM16",]$lat<- sites_spatial %>% 
    filter(site %in% c("AM16")) %>% select("lat")

df_sites[df_sites$site=="TO04",]$long<- sites_spatial %>% 
    filter(site %in% c("TO04")) %>% select("long")
df_sites[df_sites$site=="TO04",]$lat<- sites_spatial %>% 
    filter(site %in% c("TO04")) %>% select("lat")
```

#Save the files
```{r , echo=FALSE}
df_sites %>% write_csv("./data/sites_explained.csv")
```


## Exploratory Plots

You can also embed plots, for example:

```{r , echo=FALSE}

```

